Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex

%% Comments on the results:
\cref{tbl:cl_table_1} shows results
We get the best results on S-MNIST both 40 and 200 pts. per task

On S-FMNIST we are on par with DER, which is however exploiting a reservoir buffer technique, that iteratively samples new "inducing points"

On P-MNIST we are lower than S-FSVI, however % I'm still running experiments, so we can hope that it is not the best overall in the end

>>>>

%% Comments on the results:
From \cref{tbl:cl_table_1}, it is clear that the objective methods completely fail compared to the function-space methods on S-MNIST and S-FMNIST, where the tasks are composed of disjoint set of classes, but they are still able to retain previous performance on P-MNIST where the challenge is to contrast the domain shift over the tasks. %, commonly referred as Domain Incremental Learning. (opposed to the Class-Incremental Learning for S-MNIST and S-FMNIST)
Considering the function-space methods, we can see that \our achieves the best results on both settings on S-MNIST, where the condensing the information coming from the entire task datasets $\dataset_t$ is particularly effective, when using fewer points per task.
On S-FMNIST, our method obtains close results to DER, which regularizes the model by taking the mean squared error between current and old function outputs without accounting the covariance structure of the loss but assumes an i.i.d. prior similar to our L2 ablation. Moreover, their method exploits reservoir sampling \citep{vitter1985random} to obtain a continuously updated set inducing points.
S-FSVI obtains the best on P-MNIST, but with the downside of requiring high computational costs, compared to \our. \todo{on PMNIST our method is not really super-fast, so that could be not the best thing to say here} % we could also say that P-MNIST is known to be a bad/ill-posed dataset for CL 
Finally, it is worth noticing as our ablation already provides a very solid baseline consistently over all datasets.
